Structural controllability of ecological networks

### 2018-06-26 paper/manuscript.Rmd
edits and comments about captions of figs 2 and 3

```{r fig-control-configuration, fig.height=fig_control_config$height, fig.width=fig_control_config$width,fig.cap = "Maximum matchings and control configurations. In directed networks, a maximum matching is the largest possible set of links that do not share start or end nodes (dark purple). Maximum matchings are not necessarily unique, instead, each of them is related to a possible minimum driver-node set in the network (the nodes to which an external control input, in orange, should be applied in order to ensure controllability). The size of the minimum driver-node set *D* corresponds exactly to the number of unmatched nodes (the number of nodes in the network *N* minus the matching size). To account for network size, we use the size of the minimum driver-node set relative to the total number of nodes *n~D~ = D/N* as a measure of the extent to which the network structure can be harnessed to control the system."}
replayPlot(fig_control_config$plot)
```

@@

```{r fig-emp-controllability, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap="(a) Density plot of the relative size of the minimum driver-node set $n_D$ in the invaded (light) and uninvaded (dark) empirical networks. (b) The relationship between the asymmetry plant/pollinator richness and $n_D$. The plot shows the values predicted by the most parsimonious model. (c) The density distribution of the difference between the relative size of the minimum driver-node set of random networks and that of empirical networks. We randomised either the species visitation patterns (light line) or randomised the direction of control between a species pair (dark line). The vertical dashed lines indicate the median values of each distribution."}
drake::loadd(fig_emp_controllability)
fig_emp_controllability %>%
  purrr::map(function(x) x + theme(plot.margin = grid::unit(c(0.5, 1.5, 0.5, 1.5), "mm"))) %>% {
    cowplot::plot_grid(plotlist = ., 
                     nrow = 1, 
                     align = "h")
  }

>>>>

```{r fig-control-configuration, fig.height=fig_control_config$height, fig.width=fig_control_config$width,fig.cap = "Maximum matchings and control configurations. In directed networks, a maximum matching is the largest possible set of links that do not share start or end nodes (dark purple). Maximum matchings are not necessarily unique; instead, each of them is related to a possible minimum driver-node set in the network (the nodes to which an external control input, in orange, should be applied in order to ensure controllability). The size of the minimum driver-node set *D* corresponds exactly to the number of unmatched nodes (the number of nodes in the network *N* minus the matching size). To account for network size, we use the size of the minimum driver-node set relative to the total number of nodes *n~D~ = D/N* as a measure of the extent to which the network structure can be harnessed to control the system."}
replayPlot(fig_control_config$plot)
```

@@

<!-- DBS: I don't understand the description of (b) below about the values predicted by the most parsimonious model. I think it needs more info to be fully intelligible. -->
```{r fig-emp-controllability, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap="Drivers of network controllability. (a) Probability density of the relative size of the minimum driver-node set $n_D$ in the invaded (light) and uninvaded (dark) empirical networks. (b) The relationship between the asymmetry plant/pollinator richness and $n_D$. The plot shows the values predicted by the most parsimonious model. (c) Probability density of the difference between the relative size of the minimum driver-node set of random networks and that of empirical networks. We randomised either the species visitation patterns (light line) or randomised the direction of control between a species pair (dark line). The vertical dashed lines in (a) and (c) indicate the median values of the distributions."}
drake::loadd(fig_emp_controllability)
fig_emp_controllability %>%
  purrr::map(function(x) x + theme(plot.margin = grid::unit(c(0.5, 1.5, 0.5, 1.5), "mm"))) %>% {
    cowplot::plot_grid(plotlist = ., 
                     nrow = 1, 
                     align = "h")
  }
